\documentclass[11pt]{report}

\usepackage{fullpage}
\usepackage{array}
\renewcommand{\labelenumi}{(\arabic{enumi})}
\renewcommand{\labelenumii}{\alph{enumii}}
\renewcommand{\labelenumiii}{\roman{enumiii}}
\newcommand{\heading}[1]{{\subsubsection*{\hfill#1\hfill\phantom{tab}}}}
\newcommand{\PreserveBackslash}[1]{\let\ttemp=\\#1\let\\=\ttemp}
\let\PBS=\PreserveBackslash
\newcommand{\lefttblcol}{\PreserveBackslash\raggedright\hspace{0pt}}
\newcommand{\righttblcol}{\PBS\raggedleft\hspace{0pt}}
\newcommand{\centretblcol}{\PBS\centering\hspace{0pt}}
\newcolumntype{P}[1]{>{\lefttblcol}p{#1}}

\makeatletter
\renewcommand{\chapter}{\@startsection{chapter}{1}{0mm}{\baselineskip}{0.5\baselineskip}{\centering\sc\large}}
\renewcommand{\section}{\@startsection{subsection}{2}{0mm}{-\baselineskip}{0.5\baselineskip}{\normalfont\large\bf}}
\makeatother
\renewcommand{\thesubsection}{\arabic{subsection}}
\renewcommand{\thesection}{Chapter \arabic{chapter}}

\title{Constitution of Drag and Drop}


\author{https://github.com/DragandDrop-wsu}

\date{\today}

%\date{Assented on <date>; date of commencement <date>.}

\setcounter{tocdepth}{1}


\begin{document}
	\maketitle
	
	
	
	% \noindent
	% To be read in light of the following amendments:
	
	% \begin{tabular}{l}
	%     Amendment 1\\
	%     Amendment 2\\
	%     Amendment 3\\
	% \end{tabular}
	
	\noindent
	
	\tableofcontents
	
	\newpage
	\noindent
	To introduce a Constitution for the Drag and Drop student club and guideline for proceedures.
	
	\chapter{Article I: Name}
	
	\section*{\S1}
	The name of this organization shall be Drag and Drop, stylized and henceforth referred to as DAD.
	
	\chapter{Article II: Purpose}
	\section*{\S1}
	The purpose of this organization shall be as follows:
	
	\begin{enumerate}
		\item Creating a bridge between STEM and non-STEM students.
		\item Promoting the dignity, and achievements of the STEM field.
		\item Creating a safe space where those with questions about STEM can ask freely and openly.
	\end{enumerate}
	
	%	\chapter{Article III: Affiliations}
	%	\section*{\S1}
	%	This organization is affiliated with x.
	
	\chapter{Article III: Membership}
	\section*{\S1}
	The membership of DAD shall consist of currently enrolled Wright State University students.
	\section*{\S2}
	Membership of this organization follows all University policies. Including but not limited to, academic integrity and Title IX.
	\section*{\S3}
	Membership (intial entry) of DAD requires two current members provide recommendations for the person, this is henceforth known as the eligibility requirement.
	\section*{\S4}
	Membership responsibilities require that the Constitution is respected to the fullest extent. 
	
	More general responsibilities are as follows:
	\begin{enumerate}
		\item Attend at least one meeting a semester.
		\item Introduce other students to DAD.
		\item Brainstorm and help run events.
		\item Assist in helping aquire funds for the club.
	\end{enumerate}
	
	\section*{\S5}
	Membership may be terminated by the following:
	\begin{enumerate}
		\item Insubordination towards the Constitution.
		\item Unexcused lack of attendence to events held by DAD as defined by the minimum in general responsibilties.
		\item Hostile behaviour towards other members.
	\end{enumerate}
	\chapter{Article IV: Officers}
	\section*{\S1}
	The officers of the organization shall consist of:
	\begin{enumerate}
		\item President
		\item Vice President
		\item Secretary
		\item Treasurer
		\item General Officer(s)
	\end{enumerate}
	
	\section*{\S2 --- Qualifications}
	
	\subsection*{\S2.1 --- President}
	\begin{enumerate}
		\item Belong or intend to be apart of a STEM department.
		\item Must have attended Wright State University for at least one academic year.
		\item Must have not been found guilty of any academic dishonesty.
	\end{enumerate}
	\subsection*{\S2.2 --- Vice President}
	The qualifications for the Vice President shall be the same as the President.
	\subsection*{\S2.3 --- Secretary}
	There are no requirements for the secretary.
	\subsection*{\S2.4 --- Treasurer}
	\begin{enumerate}
		\item Must not have a criminal record.
		\item Must be a citizen of United States.
	\end{enumerate}
	\subsection*{\S2.5 --- General Officer}
	There are no requirements for the general officer.
	
	\section*{\S3 --- Description \& Duties}
	
	\subsection*{\S3.1 --- President}
	\begin{enumerate}
		\item Preside at all non-leisure meetings.
		\item In a matter of a tie, votes along with the Vice President, and Advisor to break the tie.
		\item Represents the club in front of the Wright State student body.
		\item Attend regular meetings, executive board meetings as often as schedule allows.  
		\item Assist in the orientation of new officers.
		\item Maintain contact with the Student Life Office.  
	\end{enumerate}
	\subsection*{\S3.2 --- Vice President}
	\begin{enumerate}
		\item Follow directives ordered by the President, and Advisor in relation to DAD.
		\item In a matter of a tie, votes along with the President to break the tie.
	\end{enumerate}
	\subsection*{\S3.3 --- Secretary}
	\begin{enumerate}
		\item Catalogues meetings.
		\item Keeps a record of all members, past and current.
		\item Ensures each meeting has a sign-in roster, which will be tabulated to represent attendance rate and then recorded (both digitally and paper).
		\item Assists to the needs of the treasurer during itemisation of a meeting.
	\end{enumerate}
	
	\subsection*{\S3.4 --- Treasurer}
	\begin{enumerate}
		\item Raises capital or current expenditure for the club.
		\item Holds and controls all funds.
		\item Responsible for tabulating fiscal data and itemising expenditures.
		\item Holds DAD in the exercise of its legislative and executive authority in regard to any matter that may have fiscal impact.
	\end{enumerate}
	
	\subsection*{\S3.5 --- General Officer}
	\begin{enumerate}
		\item Academic year auditing ensuring all offices are following the Constitution.
		\item Ensures that each member of DAD has knowledge of the Constitution.
		\item As the General Officer office is a two person office, each officer must keep the other in line with the Constitution.
	\end{enumerate}
	
	\section*{\S4 --- Selection}
	
	Officers are to be selected by the club through a democratic process. An election committee will devise the technical process of how voting will take place (for example using a key based system like PGP or GPG); however, a minimum of the following must be met:
	
	\begin{enumerate}
		\item Each vote can be validated as coming from a member of DAD.
		\item Each vote is anonymous.
		\item Each vote is equal.
	\end{enumerate}
	
	In terms of eligibility for each office see Article IV: \S2. Elections occur each academic year, the first period which requires a two-thirds majority in order to move into the officer selection election. The first period occurs third week of January. The officer selection election period occurs during the second week of February. Terms for each office do not expire until a officer selection election occurs, in which then there will be a transition month, where the previous officers have time to hand off their roles and inform the newly elected.
	
	\section*{\S5 --- Vacancy}
	
	Should an officer's position become vacant during his/her term, the following shall take place:
	
	If the President office becomes vacant, the Vice President shall assume the position. The election committee should begin the process in order to hold an election for solely the Vice President office.
	
	If any of the Vice President, Secretary, Treasurer, and General Officer offices becomes vacant, the election committee should begin the process in order to hold an election for solely the vancancies.
	
	\section*{\S6 --- Termination}
	
	In case of termination/removal of an officer, vacancy rules shall apply to filling the terminated officer. 
	
	
	Termination from being an officer does not remove membership from DAD; however, terminiation does remove any eligiabilty in running for any office.
	
	Should an officer of any office commit any of the following:
	\begin{enumerate}
		\item cronyism
		\item infidelity
		\item lack of involvement
	\end{enumerate}
	... can warrent termination of said officer.
	
	
	\chapter{Article V: Advisor}
	\section*{\S1 --- Requirements}
	Our organization advisor, must be a member of the faculty, administration, or staff of Wright State University.
	
	\section*{\S2 --- Responsibilities}
	
	\begin{enumerate}
		
		\item Maintain an awareness of the activities and programs sponsored by the student club.  
		\item Meet on a regular basis with the leader of the student club to discuss upcoming meetings, long range plans, goals, and problems of the club.    
		\item Explain and clarify campus policy and procedures that apply to the club.  
		\item Provide direction in the area of parliamentary procedure, meeting facilitation, group building, goal setting, and program planning.
		\item Assist the club treasurer in monitoring expenditures, fund raising activities, and corporate sponsorship to maintain an accurate and up to date account ledger.  
		\item Inform club members of those factors that constitute unacceptable behaviour on the part of the club members, and the possible consequence of said behaviours.  
	\end{enumerate}
	
	\section*{\S3 -- Vacancy}
	Should the position of advisor become vacant during the year, the President of DAD shall seek out another advisor.
	
	\section*{\S4 --- Termination}
	Termination of an advisor requires an election, with a two-thirds majority. Such a process can be started by two members of DAD that hold an office position.
	
	\chapter{Article VI: Meetings}
	\section*{\S1 Regular Meetings}
	Meetings which are to be considered leisure, at least one an academic semester shall happen. One week notice must be given in advance. Any member of DAD can announce such a meeting so long as any office is informed.
	\section*{\S2 Special Meetings}
	Meetings which are considered to be an official meeting of DAD. Meetings may involve a speaker and are aimed to be focused around the purpose of DAD as defined in Article II: \S1. Each member must attend at least one of these meetings if they are held. Only members which belong to an office may announce such a meeting. Notice will be given two weeks in advance.
	\section*{\S3 Operation Meetings}
	Meetings which are purposed to improve DAD, open floor to the larger community to discuss any ideas. One such meeting shall occur every academic year. Only members which belong to an office may announce such a meeting. Notice will be three weeks in advance.
	\chapter{Article VII: Committees}
	TODO
	\chapter{Article VIII: Amendments}
	TODO
	
	
\end{document}